\documentclass[12pt,a4paper]{article}

% Margins.
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{0pt}
\setlength{\topmargin}{-60pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10.75in}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}	% Clickable links to figures, references and urls.
\usepackage{datetime}
\usepackage{longtable}

% Drawing.
\usepackage{pgf}
\usepackage{tikz}

% Listings for formatting code.
\usepackage{listings}
\usepackage{textcomp}
% General options.
\lstset{breaklines=true, basicstyle=\small\ttfamily, tabsize=4, numbers=left, stepnumber=1, frame=single, showstringspaces=false, upquote=true}
% C++ specific high-lighting. Comments are 50/50 shades of green/black and strings coloured with 60/40 red/black mixture.
\lstset{language=[ISO]C++, commentstyle=\color{green!50!black}, keywordstyle=\color{blue}, stringstyle=\color{red!60!black}}

%opening
\title{Data Structures and Algorithms\\Class 08\\Stacks and Queues}
\author{Attique Dawood}
\date{February 24, 2015\\[0.2cm] Last Modified: \today, \currenttime}
\begin{document}
\maketitle
\section{Announcements}
\begin{itemize}
\item None.
\end{itemize}
\section{Revision}
\begin{itemize}
\item Empirical analysis.
\item 2D array storage.
\item Doubly--linked list.
\end{itemize}
\section{Stack~\cite[Sec. 2.3]{Aho}}
Stack is an ADT where all insertions and deletions take place at one end called the $top$. Following operations are defined for a stack ADT:
\begin{itemize}
\item \verb|Top()|: Gives the value at the top of stack.
\item \verb|Pop()|: Deletes the top--most value.
\item \verb|Push(x)|: Insert $x$ at the top of stack.
\item \verb|MakeNULL()|: Empties stack by popping out all values.
\item \verb|IsEmpty()|: Checks if stack is empty or not. Returns true or false.
\end{itemize}
\section{Text Editor Example}
A text editor records keystrokes and processes them. The text editor can be implemented using a stack.
\section{Stack and Heap in Memory Allocation}
Static variables are allocated memory at compile time. These are stored in a segment of memory known as stack. Dynamic memory allocations take place in another memory segment known as the heap.
%\section{Exercises}
%\noindent\textbf{Question:} ?\\[0.2cm]
%\nocite{*}
\bibliographystyle{plain}
\bibliography{DSRef}
\end{document}
