\documentclass[12pt,a4paper]{article}

% Margins.
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{42pt}
\setlength{\topmargin}{-54pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10in}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}	% Clickable links to figures, references and urls.
\usepackage{datetime}
\usepackage{longtable}
\usepackage{subfigure}

% Links direct to top of figures.
\usepackage[all]{hypcap}

% Drawing.
\usepackage{pgf}
\usepackage{tikz}

% Listings for formatting code.
\usepackage{listings}
\usepackage{textcomp}
% General options.+++
\lstset{breaklines=true, basicstyle=\small\ttfamily, tabsize=4, numbers=left, stepnumber=1, frame=single, showstringspaces=false, upquote=true}
% C++ specific high-lighting. Comments are 50/50 shades of green/black and strings coloured with 60/40 red/black mixture.
\lstset{language=[ISO]C++, commentstyle=\color{green!50!black}, keywordstyle=\color{blue}, stringstyle=\color{red!60!black}}

%opening
\title{\vspace{-2cm}Physics for Engineers\\Class 19\\Electric Field Due to Ring and Disk of Charge}
\author{Attique Dawood}
\date{September 30, 2013\\[0.2cm] Last Modified: \today, \currenttime}
\begin{document}
\maketitle
\section{Announcements}
\begin{itemize}
\item None.
\end{itemize}
\section{Continuous Charge Distributions}
In real life charges mostly appear bunched in different formations resembling the shape of the object on which they reside. It is more practical to think of continuous charge distributions rather than individual point charges.

\begin{equation}
dq=\rho_Ldl,
\end{equation}
\begin{equation}
dq=\rho_SdS,
\end{equation}
and
\begin{equation}
dq=\rho_Vdv.
\end{equation}
Integration of differential charge expression gives the total charge.
Note: Serway and Jewet \cite{Serway} refer to these charge densities as $\lambda$, $\sigma$ and $\rho$.
\section{Exercises}
\noindent\textbf{Question 1 \cite[Example 4.4, page 117]{Sadiku}\cite[Example 23.8, page 721]{Serway}:} A circular ring of radius $a$ carries a uniform charge $\rho_L$ C/m and is placed on the $xy$--plane with axis the same as the $z$--axis. Find the electric field at a point P(0, 0, $h$) on $z$--axis.\\[0.2cm]
\noindent\textbf{Question 2 \cite[Practice Exercise 4.4, page 119]{Sadiku}\cite[Example 23.9, page 722]{Serway}:} A circular disk of radius $a$ carries a uniform charge $\rho_S$ or $\sigma$ C/m$^2$ and is placed on the $xy$--plane with axis the same as the $z$--axis. Find the electric field at a point P(0, 0, $h$) on $z$--axis.
%\nocite{*}
\bibliographystyle{plain}
\bibliography{PhysicsRef}
\end{document}
