\documentclass[12pt,a4paper]{article}

% Margins.
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{42pt}
\setlength{\topmargin}{-54pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10in}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}	% Clickable links to figures, references and urls.
\usepackage{datetime}

% Drawing.
\usepackage{pgf}
\usepackage{tikz}

% Listings for formatting code.
\usepackage{listings}
\usepackage{textcomp}
% General options.
\lstset{breaklines=true, basicstyle=\small\ttfamily, tabsize=4, numbers=left, stepnumber=1, frame=single, showstringspaces=false, upquote=true}
% C++ specific high-lighting. Comments are 50/50 shades of green/black and strings coloured with 60/40 red/black mixture.
\lstset{language=[ISO]C++, commentstyle=\color{green!50!black}, keywordstyle=\color{blue}, stringstyle=\color{red!60!black}}

%opening
\title{\vspace{-3cm}Programming for Engineers II\\Assignment 03\\Operator Overloading\\Complex Matrix Class}
\author{Attique Dawood}
\date{February 25, 2014\\Due: March 10, 2014\\[0.2cm] Last Modified: \today, \currenttime}
\begin{document}
\maketitle
\begin{enumerate}
\item Overload different operators for the \verb|Complex| and \verb|Matrix| classes from assignment 2.
\item Assignment 02 solution is provided. You can use that as a template for your assignment. Read the code carefully. Places where you need to make changes are indicated with a \verb|TODO| comment.
\item Two \verb|Makefile|s have been provided with this assignment, a simple makefile and a generic makefile. From now on, you can use the generic makefile for you assignments/projects. Keep in mind a makefile must be named \verb|Makefile| or the \verb|make| command will not recognise it.
\item Existing math functions must be replaced with operator functions.
\item Replace \verb|Input()| and \verb|Display()| functions with stream operators, \verb|<<| and \verb|>>|.
\item Copy constructor and assignment operator for \verb|Matrix| class must be overloaded so that matrix data is properly copied.
\item Overload logical operators for both classes.
\item Any other additional operators that you overload will count as bonus.
\item Using a double pointer and dynamically storing matrix data will also count as bonus. For this you  need to properly allocate and deallocate memory using \verb|NULL| checks. In addition, provide a destructor.
\end{enumerate}
\end{document}
