\documentclass[12pt,a4paper]{article}

% Margins.
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{42pt}
\setlength{\topmargin}{-54pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10in}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}	% Clickable links to figures, references and urls.

% Drawing.
\usepackage{pgf}
\usepackage{tikz}

% Listings for formatting code.
\usepackage{listings}
\usepackage{textcomp}
% General options.
\lstset{breaklines=true, basicstyle=\small\ttfamily, tabsize=4, numbers=left, stepnumber=1, frame=single, showstringspaces=false, upquote=true}
% C++ specific high-lighting. Comments are 50/50 shades of green/black and strings coloured with 60/40 red/black mixture.
\lstset{language=[ISO]C++, commentstyle=\color{green!50!black}, keywordstyle=\color{blue}, stringstyle=\color{red!60!black}}

%opening
\title{\vspace{-2cm}Programming for Engineers II\\Class 08\\Relationship Between Classes\\Association}
\author{Attique Dawood}
\date{February 08, 2013\\[0.2cm] Last Modified: \today}
\begin{document}
\maketitle
\section{Announcements}
\begin{itemize}
\item Assignment--based Quiz.
\end{itemize}
\section{Revision}
\begin{itemize}
\item Relationship between classes.
\item Inheritance: Base class and derived class.
\item Derived class inherits all attributes and functions of base class. A student has all the attributes of a person in addition to CGPA and roll number.
\item Inheritance is represented by an empty or hollow arrow--head from derived class to base class.
\item Ownership or `has a' relationship. A car \textbf{has a}n engine. A person \textbf{has a} brain.
\item Two types of ownership: composition and aggregation.
\item Composition is strong link. If life--cycle of container object ends, then contained objects are destroyed or cease to exist. A person \textbf{has a} brain. When that person dies, his brain will cease to function.
\item Aggregation is weak link. Life--cycle of contained objects does not end with that of container. For example, a person \textbf{has a} mobile phone. If that person dies, mobile will continue to function.
\end{itemize}
\section{Relationship Between Classes}
\subsection{``using a'' and ``knows a'' Relationship or Association}
\begin{itemize}
\item Represented by a single stealth arrow from `using' class to `used' class. Class being used may not be aware of class using it.
\item A person driving a car is an association between two objects. Person is `using' a car.
\item Student X and talking to student Y because they `know' each other and exchange views.
\item A remote control can interact or talk to AC.
\end{itemize}
\nocite{*}
\bibliographystyle{plain}
\bibliography{OOPref}
\end{document}
