\documentclass[12pt,a4paper]{article}

% Margins.
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{0pt}
\setlength{\topmargin}{-60pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10.75in}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}	% Clickable links to figures, references and urls.
\usepackage{datetime}
\usepackage{longtable}

% Drawing.
\usepackage{pgf}
\usepackage{tikz}

% Listings for formatting code.
\usepackage{listings}
\usepackage{textcomp}
% General options.
\lstset{breaklines=true, basicstyle=\small\ttfamily, tabsize=4, numbers=left, stepnumber=1, frame=single, showstringspaces=false, upquote=true}
% C++ specific high-lighting. Comments are 50/50 shades of green/black and strings coloured with 60/40 red/black mixture.
\lstset{language=[ISO]C++, commentstyle=\color{green!50!black}, keywordstyle=\color{blue}, stringstyle=\color{red!60!black}}

%opening
\title{Introduction to Computing\\Lab 04\\Conditional Statements}
\author{Moomal Bukhari\and Attique Dawood}
\date{March 09, 2015\\[0.2cm] Last Modified: \today, \currenttime}
\begin{document}
\maketitle
\section{Comparison Operators}
The comparison operators can be used to compare two values. The values can also be variables.  For example, \verb|x == y|. This should be read as \textit{Is x equal to y?} Most commonly used operators are:
\begin{itemize}
\item \verb|==| (equals?)
\item \verb|!=| (not equals?)
\item \verb|>| (greater than?)
\item \verb|<| (less than?)
\item \verb|>=| (equals or greater than?)
\item \verb|<=| (equals or less than?)
\end{itemize}

\section{Conditional Statements}
The syntax for conditional statement is,
\begin{lstlisting}
if (condition...)
{
    do this if condition is true...
}
else
{
    do this if condition is false...
}
\end{lstlisting}
If the condition is evaluated to be 0 then it is false. If condition is non--zero it is true.
Operators in previous section are useful for testing a certain condition. For example,
\begin{lstlisting}
int x = 2;
int y = 4;
if (x == y)
{
    cout << "x is equal to y" << endl;
}
else
{
   cout << "x is not equal to y" endl;
}
\end{lstlisting}
In this case the output will be \verb|x is not equal to y|. The \verb|else| part is not mandatory and an \verb|if| statement can be used standalone. For example,
\begin{lstlisting}
int x;
cin >> x;
if (x > 0)
{
    cout << "You have entered a positive number" << endl;
}
\end{lstlisting}
\section{Exercises/Lab Tasks}
\subsection{Task 1: SGPA Calculator}
Ask the user to input GPAs of five courses. Calculate semester GPA from GPAs of individual courses.
\subsection{Task 2: ATM Simulation}
Simulate an ATM machine using the following algorithm. Any added functionality can earn you bonus marks.
\begin{lstlisting}
VARIABLE PIN     {4 digit roll number}
VARIABLE Balance 15000
VARIABLE Input
START
	OUTPUT "Enter PIN":
	INPUT Input
	IF Input is not equal to PIN
		EXIT
	ELSE
		OUTPUT "Enter your choice"
		OUTPUT "1. Check balance"
		OUTPUT "2. Withdraw money"
		OUTPUT "3. Exit"
		INPUT Input
		IF Input is equal to 3
			EXIT
		ESLEIF INPUT is equal to 2
			OUTPUT Balance
		ELSEIF INPUT is equal to 1
			OUTPUT "How much money do you want to withdraw?"
			INPUT Input
			IF Input is greater than balance
				OUTPUT "ERROR: Insufficient funds"
			ELSE
				SUBTRACT Input from Balance
				OUTPUT Remaining balance
		ELSE
			OUTPUT "Incorrect input"
	EXIT
END
\end{lstlisting}
\end{document}