\documentclass[12pt,a4paper]{article}

% Margins.
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\headheight}{12pt}
\setlength{\headsep}{42pt}
\setlength{\topmargin}{-54pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{10in}

\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hyphens]{url}
\usepackage{hyperref}	% Clickable links to figures, references and urls.
\usepackage{datetime}

% Drawing.
\usepackage{pgf}
\usepackage{tikz}

% Listings for formatting code.
\usepackage{listings}
\usepackage{textcomp}
% General options.
\lstset{breaklines=true, basicstyle=\small\ttfamily, tabsize=4, numbers=left, stepnumber=1, frame=single, showstringspaces=false, upquote=true}
% C++ specific high-lighting. Comments are 50/50 shades of green/black and strings coloured with 60/40 red/black mixture.
\lstset{language=[ISO]C++, commentstyle=\color{green!50!black}, keywordstyle=\color{blue}, stringstyle=\color{red!60!black}}

%opening
\title{\vspace{-2cm}Programming for Engineers II\\Assignment 02\\Operator Overloading}
\author{Attique Dawood}
\date{June 25, 2013\\Due: July 01, 2013\\[0.2cm] Last Modified: \today, \currenttime}
\begin{document}
\maketitle
\noindent This is a continuation of assignment 01.
\begin{enumerate}
\item Modify the complex class to add constructor/destructor.
\item Implement arithmetic, comparison and increment/decrement operators for complex class.
\item Modify the matrix cass (of complex numbers) to include constructor/destructor.
\item Matrix data should be dynamically allocated. Make NULL pointer checks wherever appropriate.
\item Provide a resize() function so that user can resize the matrix at any time.
\item Implement the following operators for matrix class: $+, -, ==, !=$.
\item Additional marks will be allocated if you can handle 2D matrices. You should first work on making 1D matrix functional.
\end{enumerate}
A base .cpp file is provided with this assignment. You are not required to use it but it can be helpful. You must write your own code against all `TODO' comments.
\end{document}
